Title Goes Here

### 2020-04-03 analysis/paper/paper.Rmd
trimmed the chuncks a bit

library(here)

library(tidyverse)
```

@@

```{r}
#reading landmarks in tps, code from https://gist.github.com/mrdwab/2062329

@@

```{r}
#attributes of the points by calculating distance between landmakrs

@@

#gather ML and BL of all artifacts
ML = c()
BL = c()
TL = c()
SL = c()
MW = c()
TW = c()
SW = c()
for (i in 1:length(files)) {
  filename <- paste(datadir, files[i], sep = "")
  print(filename)
  landmarks <- read.tps(filename)
  ML <- c(ML, landmark_dist(landmarks, 1, 7))
  BL <- c(BL, bl_dist(landmarks))
  TL <- c(TL, tl_dist(landmarks))
  SL <- c(SL, sl_dist(landmarks))
  MW <- c(MW, landmark_dist(landmarks, 2, 11))
  TW <- c(TW, landmark_dist(landmarks, 3, 10))
  SW <- c(SW, landmark_dist(landmarks, 5, 8))
}

@@

df_sitename <- df %>% 
  mutate(files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate(files, into = c("sitename", "files"), sep = "_") %>% 
  select(-files)

@@

Correlation, Coefficient or variation, PCA
```{r}
# Correlations with significance levels
library(Hmisc)
rcorr(ML,BL, type = "pearson") # type can be pearson or spearman

@@

# Coefficient of variation (CV)
library(goeveg)
CV_ML <- cv(ML, na.rm = FALSE) #na.rm: logical. Should missing values be removed?
CV_BL <- cv(BL, na.rm = FALSE)

#PCA 
library(ggbiplot)
PCA <- prcomp(DF, center = TRUE,scale. = TRUE)

library(ggfortify) 
autoplot(prcomp(DF), data = df_sitename, colour = 'SPstage.Stage')

#https://towardsdatascience.com/principal-component-analysis-pca-101-using-r-361f4c53a9ff <- another way of PCA, relationship with two variables

###I need to figure out how to group them  -- by phase?

>>>>

library(here)
library(tidyverse)
```

@@

Reading tps data and phase information of each artifact 
```{r}
#reading landmarks in tps, code from https://gist.github.com/mrdwab/2062329

@@

Computing size attributes of the points by calculating distance between landmakrs
```{r}

@@

Gather attributes from  all artifacts
```{r}

ML = c()
BL = c()
TL = c()
SL = c()
MW = c()
TW = c()
SW = c()
for (i in 1:length(files)) {
  filename <- paste(datadir, files[i], sep = "")
  print(filename)
  landmarks <- read.tps(filename)
  ML <- c(ML, landmark_dist(landmarks, 1, 7))
  BL <- c(BL, bl_dist(landmarks))
  TL <- c(TL, tl_dist(landmarks))
  SL <- c(SL, sl_dist(landmarks))
  MW <- c(MW, landmark_dist(landmarks, 2, 11))
  TW <- c(TW, landmark_dist(landmarks, 3, 10))
  SW <- c(SW, landmark_dist(landmarks, 5, 8))
}

@@

#trim the name of each artifact.
df_sitename <- df %>% 
  mutate (files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

@@

Computing Pearson's correlation 
```{r}
# Correlations with significance levels
# I can move the library(pkg) to the top with other libraries but I'm leaving here for my reference for a while
library(Hmisc) 
rcorr(ML,BL, type = "pearson") # type can be pearson or spearman

@@

Computing Coefficient or variation
```{r}
# Coefficient of variation (CV)
library(goeveg)
CV_ML <- cv(ML, na.rm = FALSE) #na.rm: logical. Should missing values be removed?
CV_BL <- cv(BL, na.rm = FALSE)
CV_TL <- cv(TL, na.rm = FALSE)
CV_SL <- cv(SL, na.rm = FALSE)
CV_MW <- cv(MW, na.rm = FALSE)
CV_TW <- cv(TW, na.rm = FALSE)
CV_SW <- cv(SW, na.rm = FALSE)

#simpler way to calculate CV
sd(ML)/mean(ML)
```

Principal component analysis
```{r}
library(ggbiplot)

PCA <- prcomp(DF, center = TRUE,scale. = TRUE)

#group them by three phase
library(ggfortify) 
autoplot(prcomp(DF), data = df_sitename, colour = as.factor(df_sitename$SPstage.Stage))
